### 2021-11-04 README.Rmd
changes in readme

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. Later we will provide examples on how to customize the legend name.

@@

ggmatplot(x,y)
```

The next example creates a line plot of vector x against the columns of matrix y. Although the lines would be represented using different colors by default, the `color` parameter allows custom colors to be assigned to them.
The following plot assigns custom colors to the lines, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector x, and the expenditure values is used in wide format as matrix y - with its columns corresponding to the grouping structure.

The plot uses the `plot_type` 'both', which is a combination of 'point' and 'line' plots. Its customized using `ggmatplot()` parameters and a `ggplot` theme as well.

@@

```{r density}
# matrix X
x <- (iris[, 1:2])

ggmatplot(x, plot_type = "density") +
  aes(y = ..scaled..) +
  theme_bw()
```

Boxplots too accept only a single matrix or data frame, and uses its columns as individual groups. While `ggmatplot` plots are filled by default, the fill color can be made transparent by using `alpha = 0`.

@@

```{r boxplot}
# matrix X
x <- (iris[, 1:4])

@@

```{r violin}
# matrix X
x <- (iris[, 1:2])

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "Group",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap(~Group, scales = "free")
```

>>>>

The next example uses the iris dataset, with matrices `x` and `y` as shown below. The `Sepal.Length` is plotted against `Sepal.Width` and the `Petal.Length` is plotted against `Petal.Width`. Therefore the groups 'Column 1' and 'Column 2' can be interpreted as 'Sepal' and 'Petal' respectively. To make the plot more meaningful, we can add the legend label and axis names by `legend_label`, `xlab` and `ylab`.

@@

ggmatplot(x,y)
ggmatplot(x,y, 
          xlab = "Length",
          ylab = "Width",
          legend_label = c("Sepal","Petal"))
```

The next example creates a line plot of vector `x` against the columns of matrix `y` by using `plot_type = "line"`. Although the lines would be represented using different colors by default, the `color` parameter allows custom colors to be assigned to them.
The following plot assigns custom colors to the lines, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can be used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector x, and the expenditure values is used in wide format as matrix y - with its columns corresponding to the grouping structure.

The plot specifies the plot type as `plot_type = "both"`, which is a combination of 'point' and 'line' plots. It customized using `ggmatplot()` parameters and a `ggplot` theme as well.

@@

```{r density}
# matrix x
x <- (iris[, 1:2])

ggmatplot(x, plot_type = "density") +
  aes(y = stat(scaled)) +
  theme_bw()
```

Boxplots accept only a single matrix or data frame as well, and uses its columns as individual groups. While `ggmatplot` plots are filled by default, the fill color can be made transparent by using `alpha = 0`.

@@

```{r boxplot}
# matrix x
x <- (iris[, 1:4])

@@

```{r violin}
# matrix x
x <- (iris[, 1:2])

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "Group",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap( ~ Group, scales = "free")
```
